Layered Formal Verification of a TCP Stack

### 2021-09-08 SecDev21/paper.tex
taille du code

\begin{table}[!t]
    \caption{Comparison of the number of ASM instructions between the C and the SPARK implementation}
    \label{table:instr}
    \renewcommand{\arraystretch}{1.3}
    \centering
    \begin{tabular}{lcc}
    \hline
    \multirow{2}{*}{Function}&\multicolumn{2}{c}{Number of ASM instructions} \\
    &C&SPARK\\ \hline
    \spark{TCP_Listen}   & 18                  & 11                   \\
    \spark{TCP_Accept}   & 153                 & 167                  \\
    \spark{TCP_Connect}  & 103                 & 114                  \\
    \spark{TCP_Send}     & 94                  & 124                  \\
    \spark{TCP_Receive}  & 113                 & 153                  \\
    \spark{TCP_Shutdown} & 107                 & 122                  \\
    \spark{TCP_Abort}    & 42                  & 50                   \\ \hline
    \end{tabular}
\end{table}

@@

Comparing the performance of each C and SPARK functions can be random and might not reflect the real time taken by the functions due to the network latency. Instead, we have reproduced in \Cref*{table:instr} the number of ARM assembly instructions of the TCP functions written in C and in SPARK. We observe that the C functions contain less instructions and then the performance of a C code using the TCP functions will be better than the performance of the same code written in SPARK.

>>>>

\begin{table}[!t]
    \caption{Comparison of the number of ASM instructions between the C and the SPARK implementation}
    \label{table:instr}
    \renewcommand{\arraystretch}{1.3}
    \centering
    \begin{tabular}{lccc}
    \hline
    \multirow{2}{*}{Function}&\multicolumn{2}{c}{Number of ASM instructions}&\multirow{2}{*}{$\Delta$ num. of instr.} \\
    &C&SPARK & \\ \hline
    \spark{TCP_Listen}   & 18 & 11                   & $-$39\%\\
    \spark{TCP_Accept}   & 153 & 167                  & +9\%\\
    \spark{TCP_Connect}  & 103 & 114                  & +10\%\\
    \spark{TCP_Send}     & 94 & 124                  & +31\%\\
    \spark{TCP_Receive}  & 113 & 153                  & +35\%\\
    \spark{TCP_Shutdown} & 107 & 122                  & +14\%\\
    \spark{TCP_Abort}    & 42 & 50                   & +19\%\\ \hline
    \end{tabular}
\end{table}

@@

Comparing the performance of each C and SPARK functions can be random and might not reflect the real time taken by the functions due to the network latency. Instead, we have reproduced in \Cref*{table:instr} the number of ARM assembly instructions of the TCP functions written in C and in SPARK. Both C and SPARK code have been compiled with gcc by enabling the option \texttt{-Os} that performs many optimizations similar to \texttt{-O2} that do not increase the size of the generated code. We observe that the C functions contain less instructions and then the performance of a C code using the TCP functions will be better than the performance of the same code written in SPARK.
